Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-17 lloveras_2020_Albert.tex

\begin{abstract}
Observational {techniques} play an essential role in advancing our understanding of the physics of the solar corona. They provide validation data {for} three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, {key to improve} their space weather forecasting capabilities. Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale. Based on EUV data of space borne instruments, SRT allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun. We carry out a study of the corona combining tomographic reconstructions with MHD simulations {using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF). Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and the current declining phase of solar cycle 24. Tomographic reconstructions and results of the model are \albert{analysed} in distinct coronal magnetic structures. We study magnetically closed structures associated with the equatorial streamer belt, as well as magnetically open regions enclosing it. We report on the tomographic results in the different structures, their implications for the physics of the solar corona, and the {current} capability of the AWSoM model to reproduce the tomographic reconstructions in different regions.

\end{abstract}

@@

\subsection{DEMT reconstructions}\label{demt}

\noindent\notebyalbert{This section will summarize DEMT's main aspects and equations, only those needed to understand the paper. Nothing not needed to read this paper is provided. Also, no derivation of equations are provided. References are given so that the reader can dig deeper if so desires. Points to cover are:
\begin{itemize}
  \item Selected targets, instruments used. One paragraph.
  \item Characteristics of the data (specific time series, dates, bands, etc.), SolarSoft software version used for their processing. One paragraph.
  \item Technical aspects of DEMT (grid, regularization, off-limb data is only used) and how these differ from previous versions (rereferences). One paragraph.
  \item What is FBE, what is LDEM, what is R. Why we care about these three quantities and what is their physical meaning should be clear. Then the final products $\Nm$ and $\Tm$, and what is their physical meaning.
\end{itemize}
}

To perform the comparison two specific rotations were selected, CR-2082 (2009, 05 April through 03 May), a deep minimum period between solar cycles (SCs) 23 and 24 characterized by virtually no ARs, and CR-2208 (2018, 02 September through 29 September), a rotation during the early declining fase of SC 24.

To determine the thermodynamical structure of both rotations, the DEMT technique was applied to respective time series of EUV images covering each first half rotation. To study CR-2082 and CR-2208 data taken by the EUVI-B/STEREO and AIA/SDO instruments was used, respectively.

EUV images are affected by instrumental stray light contamination, which can be corrected by deconvolution of the point spread function (PSF). While in the case of AIA images there is no reliable determination of its PSF, it has been well determined for EUVI-B by \citet{shearer_2012}. For this article, all EUVI images were stray-light corrected. For the details of impact in $\Nm$ and $\Tm$, refer to \citet{lloveras_ba2017}.

In DEMT, the low corona in the height range $1.0$ to $1.25\,\mrsun$ is discretized in a spherical computational grid. The size of the tomographic cell (or voxel) is set to 0.01 \rsun \ in the radial direction, while is set 2\deg\ in both the latitudinal and longitudinal directions. We carried out a reconstruction using half of a solar rotation blocking the lines-of-sight comming from the disk (i.e. only using off-limb data).

Using the high cadence of data available, one image every 10 minutes were used. The selected images were averaged in 6-hour intervals which, given the angular resolution, is the cadence needed to fully constrain the inversion problem, for a total of about 55 images to cover a half solar rotation. For both rotations, the first 14 days of data were used.

\diego{ DONDE QUEDA MEJOR COMENTAR ESTA MEJORA?
Unlike in previous works, a 3D regularization scheme was applied, thus spurious artifacts (nduced by the previous longitude latitude regularization schemei) were minimized in the first two heights of the tomographic grid.}

We refer the reader to \citet{frazin_2009} for a detailed description of the technique, and to \citet{vasquez_2016} for a recent review on all published work based on it. Here we summarize the key points. The technique involves two consecutive procedures.

In a first step, the time series of EUV images is used to solve a SRT problem, for each EUV band independently. As a result, the 3D distribution of the so called {filter band emissivity} (FBE) is determined for each band separately. The FBE, {an emissivity-type quantity}, is defined as the wavelength integral of the coronal EUV spectral emissivity and the telescope's passband function of each EUV channel. Line-of-sight (LOS) integration of the FBE provides synthetic images that can be quantitatively compared to the real data in the time series. To find the FBE, the tomographic problem is posed a global optimization problem in which the quadratic norm of the difference between all pairs of synthetic and real images is minimized. Spatial regularization terms are also included in the objective function as to minimize high frequency spurious artifacts that are due to the specific characteristics of the SRT sparse projection matrix \citep{frazin_2009,frazin_2000}. {Due to optical depth issues that may affect LOSs} passing very close to the limb, and to the decay of intensity with radii, the 3D maps produced by DEMT analysis typically cover the height range 1.02 to 1.23 \rsun \ \citep{frazin_2009}.

\diego{COMO INTRODUZCO EL NIVEL DE REGULARIZACION? For each instrument, the DEMT analysis involves a cross-validation study to determine the optimal level of regularization.}

{In a second step, the FBE values obtained for all bands in each voxel are used to constrain the determination of a {local differential emission measure} (LDEM) distribution, which describes the temperature distribution of the electron plasma contained in each individual tomographic grid voxel. Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}

@@

{
Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}. These non-reconstructed voxels are indicated as black voxels in the Carrington maps of the reconstructed DEMT reults in Section \ref{resu}.
}

Once the LDEM is determined at each voxel, the average squared electron density $\langle \Ne^2 \rangle$ and the electron mean temperature $\Tm$ in the voxel can be computed by taking its zeroth and first moments over temperature. More specifically, at the $i$-th voxel,

{
\begin{eqnarray}\label{momento1}
 \Nsqmi = \langle \Ne^2 \rangle_i &=& \int\,\textrm{d}T\,\LDEM_i(T),\label{Ne} \\ 
\label{momento2}
 \Tmi  = \langle \Te \rangle_i &=& \frac{1}{\langle \Ne^2 \rangle_i}\,\int\,\textrm{d}T\,T\,\LDEM_i(T),\label{Tm} 
\end{eqnarray}
}

@@

being the average relative difference between the tomographic and the synthetic FBEs. The final product of DEMT is in the form of 3D maps of the electron density and mean temperature. These relationships {were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
%\temp{Aclarar que consideramos Ne como $\sqrt{<\Ne ^2>}$.} {ALBERT: Yo creo que es mejor hablar de $\sqravgN$}

%\temp{DEMT has been improved since the previously published work. We now perform hollow-tomography with the EUV images, (definir hollow-tom) and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.} \notebyalbert{NOTA de Albert: Explicá que hacés sin justificarte. Luego aclará como se hizo eso en trabajos previos, y cual es el impacto esperado. Puedo proveer un párrafo de ejemplo, pero creo que será mejor que vos escribas como te salga y yo luego edito. Algo muy importante para todo el paper: proponete escribir ``párrafos modulares". Es decir que, con las razonables limitaciones, puedan moverse de lugar, de orden, y sigan funcionando. No definiría hollow-tomography, es un término coloquial interno nuestro. Lo correcto es que al hablar de datos mucho más arribas expliques que los datos del disco no se utilizan, pero no le des un nombre a la tomografía.}

\subsection{AWSoM simulations}\label{awsom}

\noindent\notebyalbert{This section will summarize the AWSoM model. After a first version is written we will surely require some input from the Michigan friends. Points to cover:
\begin{itemize}
  \item Data input. Link with the data input for DEMT in terms of dates, etc. One paragraph.
  \item Main physical and technical aspects (grid in particular) of the model.  One paragraph. 
  \item Explain the artificially extended TR. One paragraph.
  \item What are the products of the model we care about in this paper. One paragraph.
\end{itemize}
}

@@

\subsection{Tracing of results along fieldlines}\label{trace}

\noindent\notebyalbert{This section will explain how the AWSoM magnetic model is used to trace the thermodynamic products of both DEMT and AWSoM along the fieldlines of AWSoM. This requires covering the following points:
\begin{itemize}
  \item A first paragraph qualitatively describing the process. This includes mentioning that the AWSoM products are first interpolated into the DEMT grid.
  \item A short paragraph describing the numerical method used to trace field lines. We have a nice version of this in your previous paper.  At this point the reader should understand that for each field line we have its geometry $\mathbf{r}(s)$ as a function of the distance $s$ along the loop, with $s(1\,\mrsun)\equiv 0$. 
  \item Explain very simply how then that for each voxel the middle point of the field line is selected and assigned the DEMT and AWSoM products of that cell. At this point the reader should understand that for each field line we have: $Q[r(s)]$, where $Q$ is any given quantity from either the DEMT model (specifically $\sqravgN$ and $\Tm$) or the AWSoM model (specifically $\Ne$ and $\Te$).
  \item Explain fits to the DEMT results  $\sqravgN(r)$, $\Tm(r)$.
  \item Explain then the classification of field lines.
\end{itemize}
}

Aiming determination of the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid. Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = r{\rm d}\theta/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point. In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, for a total of $96,000$ starting points. Each traced field line is classified as ``open" if it intersects the source surface, set in this work at $r=6\,\mrsun$ (where lines become radial), or as ``closed" otherwise. In the case of closed magnetic field lines, loops {are} further classified as ``small" and ``large" upon their apex height being within or beyond the range of heights studied by DEMT, respectively.

At this stage, all DEMT and AWSoM products, electron density and mean temperature in particular, can be traced along open and closed magnetic field lines. Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one). To each sample point, the results corresponding to the tomographic voxel where it is located are assigned to it. As a result, for each field line one data point per tomographic cell is obtained. This allows to analyze how density and temperature, comming from both models, vary with height along each individual field line. This approach was firstly used by \citet{huang_2012} to study inverted temperature structures in the solar minimum corona, and later on applied by \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.

\diego{aca estoy haciendo la distincion entre la densidad y temp obtenida por demt y awsom}
For each open field line, and for each leg of the closed ones, an exponential fit was then applied to the electron density and a linear fit applied to the electron temperature. For DEMT results, the data points used were $\sqravgN(r)$ and $\Tm(r)$, in case of AWSoM the data points were $\Ne(r)$ and $\Te(r)$. The exponential and linear fit equations are described by

\begin{eqnarray}\label{Nfit}
\sqravgN &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]}\\
\label{Tfit}
\Tm &=& T_0\,+\,m\,h
\end{eqnarray}
\noindent
where $h \equiv r - 1\,\mrsun$ is the coronal height measured from the photosphere. In the electron density fit, $\l\,[\mrsun]$ is the density scale height and $N_0\,[\cminvc]$ is the electron density at the footpoint ($h=0$) of the loop. In the electron temperature fit, $m\,[\MK/\mrsun]$ is the slope and $T_0\,[\MK]$ is the electron temperature at the footpoint of the loop. The slope $m$ is the radial gradient of the electron temperature along the loop, which we denote as $m = \dr\Tm$ hereafter, being $\dr\equiv\er\cdot\nabla$ the radial derivative operator, where $\er$ is the heliocentric radial unit vector.

@@

%La temperatura en funcion de la altura a lo largo de lineas muestra comportamientos lineales. En el presente trabajo nos focalizamos en lineas con temperaturas crecientes y decrecientes en foma lineal. Es decir nos quedamos con aquellas piernas donde el coeficiente de pearson entre la temperatura y la altura (rho) cumple rho mayor 0.5 (con p-value 0.05) y de esta forma se descartan aquellas piernas en las que los resultados DEMT no pueden asegurar un cambio notable de temperatura entre la base y el apice (asi no uso la palabra isotermico y evado ese problema)

%The temperature as a function of height along legs shows linear behaviors. 
In the present work we focus on lines with increasing and decreasing temperatures in linear form. In other words, we selected those legs where the {Pearson correlation coefficient $\rho$ between temperature $T$ and radius $r$ meets $|\rhoTr| > 0.5$}. \temp{(with p-value less than 0.05)}. In this way, those legs in which the DEMT results cannot ensure a noticeable change in temperature between the base and the apex, are discarded.

The linear fit allows characterization of its variation with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg.
\diego{En realidad esta regresion lineal utiliza de por si los errores, pero luego tmb los uso para el test de hipotesis, quizas vale la pena ponerlo solo ahi.}

To measure how good the quality of the exponential fit to the electron density and the linear fit to the temperature data are, a chi-square merit function was used (see Section 15.2 \citet{recipes}). The errors were estimated in \citet{lloveras_2017}, $0.07$ MK for $\Tm$ and $4.0\,10^6 cm^{-3}$ for $\Ne$ and legs with p-value $>0.005$ were rejected.

%el p-valor es un concepto estadístico, no veo xq deberia ser explicado. Lo que si, en el paper explicare bien las hipotesis nulas y de esa forma el p-valor queda bien claro.
%El p-valor es una cuantificacion de con cuanta probabilidad de exito estas rechazando o aceptando una hipotesis en particular que se la suele denominar hipotesis nula.
%En este caso, con 95$\%$ de seguridad estas rechazando las piernas que tienen un $pearson_x,y = 0$. Es decir te estarias quedando con aquellas que tienen una dependencia lineal entre x e y.
%En el segundo caso, el test de hipotesis seria sobre la hip nula de que los datos provienen una funcion distribucion donde la recta fiteada de esos datos es el valor esperado de la distribucion. Con lo cual hacerle un test chi cuadrado te da una idea de cuan acertado o no es el ajuste. En este caso la hipotesis nula es que los datos provienen de esa distrib, con lo cual el chi deberia dar bajo y descartas los que dan valores altos con un 95$\%$ de seguridad. Eso es lo que representa el p-valor =0.05 en este caso (el area bajo la funcion distribucion, es decir, probabilidad).

{To be selected a leg must meet all following conditions.}

\begin{enumerate}

\item 
The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg.

\item 
The {value of the Pearson correlation coefficient meets $|\rhoTr| > 0.5$.}

\item 
The p-value of both the exponential and linear fit must be less than 0.05.

\end{enumerate}

\albert{Coronal magnetic structures for which their temperature increases/decreases with height (in the inner corona) have been dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies. As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop. Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}. In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and considering time-averaged heating rates.}

\albert{To characterize the global thermodynamic state of the inner solar corona in distinct magnetic structures, the DEMT and AWSoM results were traced along the magnetic field lines of the latter model. Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types in this work:}

\diego{Hice las definiciones con gradiente de temperatura para que quede mas claro, pero en realidad uso el pearson.} \notebyalbert{Charlemos los tres en persona de esto.}

\begin{itemize}
 \item Type 0 - Small (meaning with apex within the DEMT range of heights) closed field lines in the latitudes range $[-30\mdeg,+30\mdeg]$ and $\dr \Tm < 0$. %This class thoroughly populates the equator of the Streamer belt during a minimum solar rotation.

\item  Type I - Small closed field lines in all latitudes, with $\dr \Tm > 0$. %This class thoroughly populates the inner of the Streamer belt.

\item  Type II - Large closed field lines (meaning their apex surpasses the DEMT range of heights) in the latitudes range $[-90\mdeg,-30\mdeg] \cup [+30\mdeg,+90\mdeg]$ and $\dr \Tm > 0$. %This class is mostly populated by very large trans-equatorial field lines forming the envelope of the Streamer belt.

\item Type III - Open field lines (meaning with apex out the DEMT range of heights) in the latitudes range $[-90\mdeg,-60\mdeg] \cup [+60\mdeg,+90\mdeg]$ and $\dr \Tm > 0$.

\end{itemize}

\albert{In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed.}

\subsection{{Energy input flux}}\label{energia}

\noindent\notebyalbert{This section will summarize how loop integrated energy quantities are computed from the DEMT products and the AWSoM magetic model alone. The summary will not include any derivation and will refer to Cecilia's paper. Only the results that are relevant are to be explicited. Start by explaining the model and assumptions, and end up summarizing the loop-integrated products (radiative and conductive fluxes). At the end the reader should understand that their sum is the enery input flux required at the coronal base to maintain the loop stable. This should be a very short section, as it is a summary of one previous paper alone.}

%correcciones a hacer! DIEGO
%Los términos de la Eq (10) requieren ser explicados. La explicación a conituación no es clara, y de hecho está mal escrita. La Eq. (7) se integra en el VOLUMEN CORONAL COMPLETO de cada tubo de flujo y se divide por el área basal del mismo. Utilizando la condición solenoidal de B se llega a la Eq. (7), dónde... y ahí deberían darse las expresiones de Phir y Phic porque no pertenecen a la literatura estandard, y explicar a continuación como todos los elementos de esas dos expresiones surgen de los fits de DEMT y del modelo magnético de AWSoM. Donde si se puede ahorrar mucho espacio es en lo previo, la Eq (8) podría no incluirse por ejemplo. Creo que ahora lo mejor es que trates de completar la explicación dando las expresiones de Phir y Phic, y luego vemos de como limarla, probablemente eliminando la ec. (8). y además el texto puede compactarse, corregirse y reordenarse mucho. Poné las unidades de las cantidades Phi entre paréntesis a continuación de $\Phi_{h,r,c}$.

Due the difference between temperatures of transition region and solar corona, there must to be a heating mechanism that compensate all the losses present in the atmosphere and maintain stable the plasma temperature. Previous works have studied this mechanism by observations and modeling, but mostly for active regions. \citet{maccormack_2017} have developed a technique that estimate the heating injected into the loops during a period of minima activity. Using DEMT combined with an extrapolation of magnetic field, as we detailed before, they obtain the different plasma parameters along each magnetic loop, and therefore, compute the energy input flux required to maintain them stable.
The model assume a simple energy balance for each magnetic flux tube, where the losses by radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated by some coronal heating power($E_h$) \citep{aschwanden_2004}:

@@

{The energy balance given by Equation (\ref{Balance}) is then integrated in the volume of any given coronal magnetic flux tube. Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a field-line integrated version of that energy balance is found,
\begin{equation}\label{FluxBalance}
\phi_h = \phi_r + \phi_c.
\end{equation}
\noindent
where the line integrated flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},} \\

@@

\section{Discussion}\label{discu}

>>>>

\begin{abstract}
Observational techniques play an essential role in advancing our understanding of the physics of the solar {corona, providing in particular validation data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere. Solar rotational tomography is currently the sole observational technique that provides a 3D quantitative description of the solar corona at a global scale.} Based on EUV data of space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights {below $\approx 1.25\,\mrsun$. We} carry out a study of the corona combining {DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling {Framework}. Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the declining} phase of SC 24. The 3D tomographic and MHD models are analysed and compared in distinct coronal magnetic structures. {We report in quantitative detail on the 3D thermodinamic structure of the inner corona as revealed by the DEMT analysis. We show in particular the existence of diverse types of temperature structures in the low and mid latitudes of the streamer belt, and that the heating energy required to keep them stable may be accounted for by Alfvén waves. We show that the latest version of the AWSoM model results agree with DEMT reconstructions to within a $\approx 20\%$ accuracy or better. We report on aspects of the AWSoM model that could be improved to better reproduce the DEMT results, in particular concerning the source region of the fast/slow solar winds.}
\end{abstract}

@@

\subsection{{DEMT Reconstructions}}\label{demt}

{We carried out the 3D DEMT reconstruction and MHD modeling of two target Carrington rotations (CR). We selected CR-2082 (2009, 05 April through 03 May), a deep minimum rotation between solar cycles (SC) 23 and 24, and CR-2208 (2018, 02 September through 29 September), a rotation during the early declining fase of SC 24. To study CR-2082 and CR-2208 data taken by the STEREO/EUVI-B and SDO/AIA instruments was used, respectively. The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package. For this work, we introduced two improvements in the implementation of the DEMT technique, as described next.}

{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we opted to only use off-limb data. In this way, the smallest scale and brighter coronal features seen on disk (most typically in the 171\AA\ band) are not included. This has two implications. Fistly, the fast dynamics that typically characterizes those structures is abscent from the data. Sencondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume. As a result, coronal dynamics induced artifacts are reduced compared to previous DEMT reconstructions.}
.
{The solution of the tomographic problem involves a very large sparse matrix. Such type of inversion problems are characterized by spurious high-frequency artifacts in the solution, which can be mitigated through \emph{regularization} techniques \citep{frazin_2000}. In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude. Also new to the present work, is the implementation of an expanded 3D regularization scheme, which adds to the previous scheme a finite difference matrix operator to approximate radial derivatives. In this way, the tomographic inversion problem is performed penalizing nonphysical high-frequency artifacts in all three spatial directions. As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.}

{We summarize next the main aspects of DEMT required for the analysis of this work. We refer the reader to \citet{frazin_2009} for a full description of the technique.}

In a first step, the time series of EUV images is used to solve a solar rotational tomography (SRT) problem, for each EUV band independently. As a result, the 3D distribution of the so called \emph{filter band emissivity} (FBE) is determined for each band separately. The FBE, {an emissivity-type quantity}, is defined as the wavelength integral of the coronal EUV spectral emissivity and the telescope's passband function of each EUV channel. Line-of-sight (LOS) integration of the FBE provides synthetic images that can be quantitatively compared to the real data in the time series. To find the FBE, the tomographic problem is posed a global optimization problem in which the quadratic norm of the difference between all {pairs of synthetic and real images is minimized.}

{In a second step, the FBE values obtained for all bands in each voxel {of the tomographic grid are used to constrain the determination of the LDEM which, as described in Section \ref{intro}, describes the temperature distribution of the plasma within the individual voxel.} Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}

@@

\noindent
{where $K$ is the number EUV bands, and $\TRF^{(k)}$ is the \emph{temperature response function} of the $j$-th detector. The TRFs are here computed based on the (known) channel’s passband times the coronal emissivity at that temperature (normalized by the squared electron density). The emissivity model used here is provided by the latest version of the CHIANTI atomic database and plasma emission model \citep{delzanna_2015,landi_2013}.}

Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}. These non-reconstructed voxels are indicated {in black color in the latitude-longitude (Carrington) maps of DEMT} reults in Section \ref{resu}.

{In this work,} data from thre EUV bands was {used:} 171, 193 and 211 \AA \ in {the} case of AIA, and 171, 195 and 284 \AA \ bands in {the} case of EUVI. When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict the tomographic emissivities \citep{frazin_2009,nuevo_2015}. In each tomographic voxel the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that allow to best reproduce the three tomographically reconstructed values of FBE in that voxel.

Once the LDEM is determined at each voxel, {the LDEM-averaged squared electron density $\Nm^2$ and electron temperature $\Tm$} in the voxel can be computed by taking its zeroth and first moments over temperature. More specifically, at the $i$-th voxel,
{
\begin{eqnarray}\label{momento1}
 \Nsqmi = \langle \Ne^2 \rangle_i &=& \int\,\textrm{d}T\,\LDEM_i(T),\label{Ne} \\ 
\label{momento2}
 \Tmi  = \langle \Te \rangle_i &=& \frac{1}{\langle \Ne^2 \rangle_i}\,\int\,\textrm{d}T\,T\,{\LDEM_i(T).}\label{Tm} 
\end{eqnarray}
}

@@

\noindent 
{being the} average relative difference between the tomographic and the synthetic FBEs. {The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.}

\subsection{{AWSoM Simulations}}\label{awsom}

\noindent\notebyalbert{This section will summarize the AWSoM model. Chip, Nishtha, do you think you could provide 2 or 3 paragraphs? We believe the points to cover are:
\begin{itemize}
  \item Data input. Link with the data input for DEMT in terms of dates, etc. One paragraph.
  \item Main physical and technical aspects (grid in particular) of the model.  One paragraph. 
  \item Explain the artificially extended TR. One paragraph.
  \item What are the products of the model we care about in this paper ($N_e$, $T_e$, $B$, $V$, as of now). One paragraph.
\end{itemize}
}

@@

\subsection{{Tracing Results Along Magnetic Fieldlines}}\label{trace}

{To determine} the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid. Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = r{\rm d}\theta/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point. In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, for a total of $96,000$ starting points.

{For analysis purposes, {the traced magnetic field lines are classified as open or closed according to their full geometry. Each closed field} line is further classified as ``small" or ``large", according to its coronal length $L$ being {respectively smaller or larger than the median value of the whole population, which is ${\rm Md}(L)\approx 0.5\,\mrsun$ for both rotations.} Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (i.e. their location at $r=1\,\mrsun$) to its apex (i.e., the location of maximum height).}

At this {stage, DEMT and AWSoM products} can be traced along open and closed magnetic field lines. Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one). To each sample point, the results corresponding to the tomographic voxel where it is located are assigned to it. As a result, for each field line one data point per tomographic cell {is obtained. This approach} was firstly used by \citet{huang_2012} to {study temperature} structures in the solar minimum {corona and by} \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.

For each open field line and {for each closed field leg}, an exponential fit {was applied} to the electron density {data points} and a linear fit applied to the electron temperature {data points}. For {the DEMT model} the data points used were $\sqravgN(r)$ and $\Tm(r)$, and in case of {the AWSoM models} the data points used were $\Ne(r)$ and $\Te(r)$. The exponential and linear fit equations are described by

\begin{eqnarray}\label{Nfit}
\sqravgN &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]}\\
\label{Tfit}
\Tm &=& T_0\,+\,m\,h
\end{eqnarray}

\noindent
where $h \equiv r - 1\,\mrsun$ is the coronal height measured from the photosphere. In the electron density fit, $\l\,[\mrsun]$ is the density scale height and $N_0\,[\cminvc]$ is the electron density at the footpoint ($h=0$) of the loop. In the electron temperature fit, $m\,[\MK/\mrsun]$ is the slope and $T_0\,[\MK]$ is the electron temperature at the footpoint of the loop. The slope $m$ is the radial gradient of the electron temperature along the loop, which we denote as $m = \dr\Tm$ hereafter, being $\dr\equiv\er\cdot\nabla$ the radial derivative operator, where $\er$ is the heliocentric radial unit vector.

@@

{Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies. As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop. Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}. In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and {considering time-averaged heating rates.}}

{To determine if the leg of a traced field line is} of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points. We then select field lines for which the temperature {is significantly correlated with height} by requiring $|\rhoTr| > 0.5$. {To test the goodness of the fit to the temperature-height data we perform a chi-squared test \citep{recipes} considering the uncertainty of the DEMT data points, selecting legs for which the fit matches the data with a 90\% confidence level.} In this way, legs for which the DEMT temperature does not show a significant {correlation} with height, or the linear fit to temperature is {not} good enough, are {excluded from the} analysis. {The test is also applied to the density-height data points, to ensure the trend is reasonably represented by the exponential fit.} Finally, selected legs are then classified as up or down according to if $\dr\Tm > 0$ or $\dr\Tm < 0$, respectively. The linear fit allows characterization of the variation of $\Tm$ with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg. {The chi-squared test to evaluate the quality of the fits considers the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$.} In summary, to be selected a leg must meet all three following conditions:

\begin{enumerate}
\item 
The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg. {This requirement is set to ensure a reasonably spread sample of heights along the leg.}
\item 
The {DEMT temperature and height data points must meet} $|\rhoTr| > 0.5$.
\item 
{The condifence level of both the exponential and linear fits must be larger than 90\%.} 
\end{enumerate}

{To characterize the global thermodynamic state of the inner solar corona in distinct magnetic structures, the DEMT and AWSoM results were traced along the magnetic field lines of the latter model. Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types in this work:}

\begin{itemize}
\item Type 0: closed-small-down with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
\item Type I: closed-small-up with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
\item Type II: closed-large-up with footpoints in the range $|{\rm latitude}|>40\mdeg$. 
\item Type III: open with footpoint in the range $|{\rm latitude}|>60\mdeg$.
\end{itemize}

{Legs of type down turn out to have a significant population only for closed-small loops. In the case of closed-large loops and open field lines, there are very few cases of type down. Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population in each case}. \\
In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed. {As shown in Section \ref{demt_res}, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}

\subsection{{Energy Input Flux}}\label{energia}

{The high temperature of the corona requires heating mechanisms to compensate for the the losses. While the vast majority of the existing literature on coronal heating focuses on ARs, some studies have been dedicated to the heating of quiet-Sun regions. In particular,  \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to mantain them stable. The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, just as described in the previous Section \ref{trace}.}

{Consider} a simple energy balance for each magnetic flux tube, {in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated {by a} coronal heating power($E_h$) \citep{aschwanden_2004}:

@@

The energy balance given by Equation (\ref{Balance}) is then integrated in the volume of any given coronal magnetic flux tube. Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a field-line integrated version of that energy balance is found,

\begin{equation}\label{FluxBalance}
\phi_h = \phi_r + {\phi_c,}
\end{equation}

\noindent
where the line integrated flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},

@@

\section{{Discussion and Conclusions}}\label{discu}

{We carried out the 3D DEMT reconstruction and MHD modeling of the inner solar corona for two target rotations, CR-2082 and CR-2208. The first target belongs to the deep minimum epoch between SCs 23 and 24, while the latter belongs to the end of the declining phase of SC 24. The present work introduces two improvements in the implementation of DEMT, namely the use of only off-limb data in the EUV images, and the inclusion of a 3D regularization scheme. As a result of the former, artifacts introduced by coronal dynamics are mitigated, and as a result of the latter, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions. The MHD model used is here the latest version of the AWSoM component of the SWMF suite.}
